MRD_final_microbiome

### 2019-06-25 import_popln_data.Rmd
updated

setwd("~/globalmicrobiome")
mnd.incidence <- read_csv("mnd.csv",col_names = TRUE)
mnd.incidence <- as.data.frame(mnd.incidence)

mb.gather <- function (x) {
    mb.group <- data.frame("Location" = c("Central Europe","Eastern Europe","Scandinavia", "Southern Europe","UKIE","USA"), "Mean" = c(1:6)) 
  c.europe <- filter(x,Location=="Belgium"|Location=="Denmark"|Location=="Germany"|Location=="The Netherlands")
    e.europe <- filter(mnd.incidence,Location=="Poland")
    scan <- filter(mnd.incidence,Location=="Finland"|Location=="Norway"|Location=="Sweden")
    s.europe <- filter(mnd.incidence,Location=="France"|Location=="Italy"|Location=="Serbia"|Location=="Spain")
    ukie <- filter(mnd.incidence,Location=="United Kingdom"|Location=="Ireland")
    usa <- filter(mnd.incidence,Location=="United States")
    mb.group[1,2] <- mean(c.europe$Value)
    mb.group[2,2] <- mean(e.europe$Value)
    mb.group[3,2] <- mean(scan$Value)
    mb.group[4,2] <- mean(s.europe$Value)
    mb.group[5,2] <- mean(ukie$Value)
    mb.group[6,2] <- mean(usa$Value)
    return(mb.group)
    }

temp <- mb.gather(mnd.incidence)

>>>>

mb.gather <- function (x) {
    # Creates an empty data frame
    mb.group <- data.frame("Location" = c("Central Europe","Eastern Europe","Scandinavia", "Southern Europe","UKIE","USA"), "Mean" = c(1:6)) 
     # groups the countries to match the microbiome classification 
  c.europe <- filter(x,Location=="Belgium"|Location=="Denmark"|Location=="Germany"|Location=="The Netherlands")
    e.europe <- filter(x,Location=="Poland")
    scan <- filter(x,Location=="Finland"|Location=="Norway"|Location=="Sweden")
    s.europe <- filter(x,Location=="France"|Location=="Italy"|Location=="Serbia"|Location=="Spain")
    ukie <- filter(x,Location=="United Kingdom"|Location=="Ireland")
    usa <- filter(x,Location=="United States")
    # gmeans the data and put it into the data frame
    mb.group[1,2] <- mean(c.europe$Value)
    mb.group[2,2] <- mean(e.europe$Value)
    mb.group[3,2] <- mean(scan$Value)
    mb.group[4,2] <- mean(s.europe$Value)
    mb.group[5,2] <- mean(ukie$Value)
    mb.group[6,2] <- mean(usa$Value)
    return(mb.group)
    }

setwd("~/globalmicrobiome")
# files nwed to be in the owrking directory
mnd.incidence <- as.data.frame(read_csv("MND-I-B.csv",col_names = TRUE))
mnd.prev <- as.data.frame(read_csv("MND-P-B.csv",col_names = TRUE))
mnd.incidence <- mb.gather(mnd.incidence)
mnd.prev <- mb.gather(mnd.prev)
